### 2017-07-08 Bright_Stars/Submission/submission2.tex
begin revision for Sergi

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Research Synergy and Drug Development: Bright Stars in Neighboring Constellations} % Please use "title case" (capitalize all terms in the title except conjunctions, prepositions, and articles).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Samet Keserci\textsuperscript{1},
%Samet Keserci\textsuperscript{1,2\Yinyang},
Eric Livingston\textsuperscript{2},
Lingtian Wan\textsuperscript{1,\textcurrency},
Alexander R. Pico\textsuperscript{3},
%Name5 Surname\textsuperscript{2\ddag},
%Name6 Surname\textsuperscript{2\ddag},
 \& George Chacko\textsuperscript{1*}
%with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} NETE Labs, NET ESolutions Corporation, McLean, VA, USA
\\
\textbf{2} Research Intelligence, Elsevier Inc., New York, NY, USA
\\
\textbf{3} Gladstone Institutes, San Francisco, CA, USA
\\
\bigskip

@@

\textbf{FDA documents} The drugs@fda website~\cite{bibFDA} was searched for each of the five therapeutics and cited references in the medical review document were manually extracted and matched to pmids. FDA Approval Summaries published in journals by FDA staff, were available for all five therapeutics and contain cited references. If the published date of a cited reference in an Approval Summary exceeded the approval date plus two months, the publication was not included.

\textbf{Patents} For each therapeutic a single patent was identified that best represented the most relevant invention to the therapeutic at hand. Identification of this patent was performed using multiple web sources. The US patent number was then used to identify the patent and the non-patent citation list from Google Patents ~\cite{bibGooglePatents} was manually processed by searching PubMed for appropriate pmids. The accuracy of manual searches was far higher than a citation matching tool that we developed for for this purpose,and were used to generate the data in this study.

@@

\textbf{Analysis}. All data used in this study were acquired exclusively from the sources listed above. Computations were performed on infrastructure owned or leased by NET ESolutions, Elsevier, or the Gladstone Institutes. Code and scripts used in this study were written in Java, Python, and R and are archived on a publicly accessible Github repository~\cite{bibGithub}.  Network visualization was performed using Cytoscape~\cite{bibCytoscape}.

@@

@@

>>>>

%% Misc. Packages
\usepackage{changes}
\definechangesauthor[name={George Chacko}, color=orange]{gc}
\setremarkmarkup{(#2)}

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Research Synergy and Drug Development: Bright Stars in Neighboring Constellations} % Please use "title case" (capitalize all terms in the title except conjunctions, prepositions, and articles).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Samet Keserci\textsuperscript{1},
%Samet Keserci\textsuperscript{1,2\Yinyang},
Eric Livingston\textsuperscript{2},
Lingtian Wan\textsuperscript{1,\textcurrency},
Alexander R. Pico\textsuperscript{3},
%Name5 Surname\textsuperscript{2\ddag},
%Name6 Surname\textsuperscript{2\ddag},
 George Chacko\textsuperscript{1*}
%with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} NETE Labs, NET ESolutions Corporation, McLean, VA, USA
\\
\textbf{2} Research Intelligence, Elsevier Inc., New York, NY, USA
\\
\textbf{3} Gladstone Institutes, San Francisco, CA, USA
\\
\bigskip

@@

\textbf{FDA documents} The drugs@fda website~\cite{bibFDA} was searched for each of the five therapeutics. \added[id=gc,remark={response to request from editor}]{The medical review document was copied from the Review section under Approval Date(s) and History, Letters, Labels, Reviews and cited references in the medical review document were manually extracted and matched to pmids using, as search terms in the PubMed GUI, text strings from the citation that, typically, consisted of the last name of the first author, 3-5 words of the title, the year of publication, and journal name.} FDA Approval Summaries published in journals by FDA staff, were available for all five therapeutics and contain cited references. If the published date of a cited reference in an Approval Summary exceeded the approval date plus two months, the publication was not included.

\textbf{Patents} For each therapeutic\deleted[id=gc,remark=revise for clarity]{a single patent was identified that best represented the most relevant invention to the therapeutic at hand}\added[id=gc,remark=revised]{, the original patent for the therapeutic in question was identified using a combination of web searches, Google Patents, and the scientific literature}.  
\deleted[id=gc,remark=restate]{Identification of this patent was performed using multiple web sources. The US patent number was then used to identify the patent...} \added[id=gc,remark={use example}]{For example, US5521184, the original patent for imatinib was assigned to the Ciba-Geigy Corporation in 1996 listing Zimmermann as inventor. Such manual identification is greatly assisted by a knowledge of the drug development field}. The non-patent citation list for a patent was copied from Google Patents~\cite{bibGooglePatents} and manually processed by searching the PubMed GUI for appropriate pmids \added[id=gc,remark={response to request from editor}] {using text strings from the citation that, typically, consisted of the last name of the first author, 3-5 words of the title, the year of publication, and journal name. Returned hits were inspected for matches to the original citation in Google Patents and accepted only in the event of a high-degree of confidence in correctness} The accuracy of manual searches was far higher than a citation matching tool that we developed for for this purpose and were used to generate the data in this study.

@@

\textbf{Analysis}. All data used in this study were acquired exclusively from the sources listed above. \added[id=gc,remark={response to request from editor}]{Data used to generate the figures and tables in this study are available in a Mendeley Data repository~\cite{bibMendeley}}. Computations were performed on infrastructure owned or leased by NET ESolutions, Elsevier, or the Gladstone Institutes. Code and scripts used in this study were written in Java, Python, and R and are archived on a publicly accessible Github repository~\cite{bibGithub}.  Network visualization was performed using Cytoscape~\cite{bibCytoscape}.

@@

\added[id=gc,remark={expanded discussion of generalizability as per editor request}]{Here, we started with the literature directly cited in the approval process for five therapeutics, which are subject to multiple layers of independent assessment, i.e., patent awards, clinical trials, and FDA reviews that in turn contribute to the relevant literature. However, the only requirement of the current method is a starting set of articles. Any question premised upon the citation record and defined by a nucleus of articles can be addressed with this approach. The method is applicable to any other therapeutic or set of therapeutics, but also to medical devices, diagnostics, standards development, and research discoveries and protocols such as induced pluripotent (IPS) cells  or CRISPR-Cas9. Furthermore, the method is generalizable to sets of articles defined by groups of authors (e.g., consortia, programs), by institutions or departments, or by grant portfolios. The application of our method to the bibliographic record of a department, for example, would provide novel, network-based metrics by which to assess collaboration, productivity, translational impact, etc. No matter the application, the method is implicitly time-dependent, allowing one to make historical comparisons and to set future goals. Importantly, our improvements to the method as presented here allow for the analysis across sets of articles in addition to within, supporting higher level interrogations of the crosstalk and collaborations that connect groups.}

@@

\bibitem{bibMendeley}
Keserci S, Livingston, E, Wan  Lingtian, Pico A, Chacko, G.
\newblock {{B}right Stars in Neighboring Constellations v4.}
\newblock Mendeley Data http://dx.doi.org/10.17632/ysh53v7gpz.4
